Peptide retention time prediction

### 2015-12-22 retention.tex
x

>>>>

\begin{abstract}
Most methods for interpreting data from shotgun proteomics experiments
are to large degree dependent on being able to predict properties of
peptide-ions. Often such predicted properties are limited to molecular
mass and fragment spectra, but here we put focus on a perhaps
underutilized property, a peptide's chromatographic retention time. We
review a couple of different principles of retention time prediction,
and their applications within computational proteomics.
\end{abstract}

Keywords: Bioinformatics; Chromatography; Regression analysis; Mass spectrometry; Peptides
